A weakly structured stem for human origins in Africa

### 2022-01-17 paper.tex
Fixed typo

Relative cross-coalescence rates (rCCR) have recently been used to estimate
divergences between a pair of populations, as measured by the rate of
coalescence between two groups divided by the mean within population
coalescence. Simulations of rCCR accuracy, however, focus on a ‘clean split’
between populations whereby groups diverge without subsequent gene flow.
Published estimates of the earliest human divergences with rCCR, which range
from 150kya-100kya \citep{Bergstrom2021-iw}, may be significantly biased when
compared to more complex models with gene flow as inferred here. We find that
midpoint estimates of rCCR are poor estimates for population divergence, often
underestimating divergence time by 50\% or greater (e.g., Mende vs. Gumuz
$\sim$15kya compared to a true divergence of 60kya), and recent migration can
lead to the misordering of divergence events (Figure~\ref{fig:4}E). We suggest
that rCCR analyses which do not fit multiple parameters including gene flow
should be interpreted with caution.

>>>>

Relative cross-coalescence rates (rCCR) have recently been used to estimate
divergence between a pair of populations, as measured by the rate of
coalescence between two groups divided by the mean within population
coalescence. Simulations of rCCR accuracy, however, focus on a ‘clean split’
between populations whereby groups diverge without subsequent gene flow.
Published estimates of the earliest human divergences with rCCR, which range
from 150kya-100kya \citep{Bergstrom2021-iw}, may be significantly biased when
compared to more complex models with gene flow as inferred here. We find that
midpoint estimates of rCCR are poor estimates for population divergence, often
underestimating divergence time by 50\% or greater (e.g., Mende vs. Gumuz
$\sim$15kya compared to a true divergence of 60kya), and recent migration can
lead to the misordering of divergence events (Figure~\ref{fig:4}E). We suggest
that rCCR analyses which do not fit multiple parameters including gene flow
should be interpreted with caution.
